The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-09 outputs/docs/events/paper.Rmd
Add political theory paras

elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols())
hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())

@@

In the following section, we briefly describe the topic modelling approach, which is to use the CTM, which is a natural extension of the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics. More detail on the topic modelling is available for readers that may be less familiar with it in Appendix \@ref(hansardworkflow)

@@

## Latent Dirichlet Allocation
Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics. This means that each day's Hansard record needs to be classified by its topics. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods. One way to get consistent estimates of the topics discussed in Hansard is to use the LDA method of @Blei2003latent.

The key assumption behind LDA is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions. The topics are not specified *ex ante*; they are an outcome of the method. In this sense, this approach can be considered unsupervised machine learning. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. The goal is to have the words found in each day's Hansard group themselves to define topics. This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult.

As applied to Hansard, LDA considers each statement to be a result of a process where a politician first chooses the topics they want to speak about. After choosing the topics, the politician then chooses appropriate words to use for each of those topics. Statistically, LDA considers each document as having been generated by some probability distribution over topics. Similarly, each topic is considered a probability distribution over terms. To choose the terms used in each document, terms are picked from each topic in the appropriate proportion. Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) in Appendix \@ref(LDAexample) illustrate an example with five topics, two documents, and ten terms.

Gibbs sampling or the variational expectation-maximization algorithm can be used to approximate the posterior. A summary of these approaches is provided in Appendix \@ref(LDAposteriorestimation). The choice of the number of topics, *k*, drives the results and must be specified *a priori*. If there is a strong reason for a particular number, then this can be used. Otherwise, one way to choose an appropriate number is to use cross validation.

@@

The CTM output of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$. The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events. But with 40 topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.

@@

The remainder of the results refer to a topic model that had 40 distinct topics defined. The choice of 40 topics was made as a trade-off between semantic coherence and exclusivity with 40 topics performing better on both measures than 20. Measures such as residuals and held-out likelihood suggest a larger number of topics would be more appropriate. See Appendix \@ref(selecttopicnumber) for these diagnostics.

Table \@ref(tab:topwords) lists the top five words associated with each of the forty topics. The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade. Note that some topics seem to somewhat overlap with their content: for example, topics 12, 17, 22 and 23 all relate to war and conflict.

@@

The next step is...

@@

## Stopwords over time {#stopwordsgraph}
**[TBD].** Insert graph of stop words over time.

@@

# Topic modelling example and details
## Examples {#LDAexample}
For instance, if there were five topics and two documents, then the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).

@@

@@

>>>>

elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols())

top_words <- top_words %>% 
  rename(Topic = topic, Terms = terms)

hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())

@@

In the following section, we briefly describe the topic modelling approach, which is to use the CTM, which is a natural extension of the Latent Dirichlet Allocation (LDA) model [@Blei2003latent], before discussing the Bayesian hierarchical Dirichlet analysis model used to investigate changes in topics. More detail on the topic modelling is available for readers that may be less familiar with it in Appendix \@ref(LDAexample).

@@

## Latent Dirichlet Allocation
Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics. This means that each day's Hansard record needs to be classified by its topics. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.

Other work such as @BaumgartnerJones1993 and @DowdingHindmoor2010 does this by creating a standardised codebook of policy categories and sub-categories and then manually assigning text to topics as appropriate. This approach ensures the categorisation is reasonable but as it is a manual process the size of the text that can be categorised is limited. In exchange for some reduction in the reasonableness of the categorisation, the LDA method of @Blei2003latent is able to provide consistent categorisation of the topics discussed in Hansard for large text collections.

The key assumption behind LDA is that each day's text, 'a document', in Hansard is made by speakers who decide the topics they would like to talk about in that document, and then choose words, 'terms', that are appropriate to those topics. A topic could be thought of as a collection of terms, and a document as a collection of topics, where these collections are defined by probability distributions. The topics are not specified *ex ante*; they are an outcome of the method. In this sense, this approach can be considered unsupervised machine learning. Terms are not necessarily unique to a particular topic, and a document could be about more than one topic. The goal is to have the words found in each day's Hansard group themselves to define topics. This can provide more flexibility than other approaches such as a strict word count method, but can require a larger dataset and make interpretation more difficult. More detail on how LDA works is available in Appendix \@ref(LDAexample).

@@

The CTM output of interest is the proportion of each topic appearing in each document, that is, the $\theta_d$. The aim of this stage of the modelling process is to analyse how the distribution of topics changes in relation to different types of events. But with 80 topics for each of the roughly 14,551 chamber-sitting-days the data are still too noisy to easily visualise changes around events.

@@

The remainder of the results refer to a topic model that had 80 distinct topics defined. The choice of 80 topics was made as a trade-off between the standard diagnostic tests that suggested a larger number of topics would be more appropriate, and the need for the topics to be tractable for our analysis model and understandable for us. The diagnostic tests are detailed in Appendix \@ref(selecttopicnumber).

Table \@ref(tab:topwords) lists the top ten words associated with each of the 80 topics. The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade. Note that some topics seem to somewhat overlap with their content: for example, topics 12, 17, 22 and 23 all relate to war and conflict. **[UPDATE THAT.]**

@@

The next step is remove the front matter from the PDFs.

```{r frontmatterexample, echo=TRUE, eval = FALSE}
library(furrr) # May need the devtools version devtools::install_github("DavisVaughan/furrr")
library(lubridate)
library(pdftools)
library(stringi)
library(tidyverse)
library(tictoc)
library(tm)
# Set up furrr to use multiple processors
plan(multiprocess)

# Create the lists of PDFs to read and file names to save text as
use_this_path_to_get_pdfs  <- "/Volumes/Hansard/pdfs/federal/hor"
use_this_path_to_save_csv_files  <- "/Volumes/Hansard/parsed/federal/hor"

# Get list of Hansard PDF filenames
file_names <-
  list.files(
    path = use_this_path_to_get_pdfs,
    pattern = "*.pdf",
    recursive = TRUE,
    full.names = TRUE
  )
file_names <- file_names %>% sample() # Randomise the order
# Modify the savenames
save_names <- file_names %>%
  str_replace(use_this_path_to_get_pdfs, "") %>%
  str_replace(".pdf", ".csv")
save_names <- paste0(use_this_path_to_save_csv_files, save_names)

#### Create the function that will be applied to the files ####
get_text_from_PDFs <-
  function(name_of_input_PDF_file,
           name_of_output_csv_file) {
    pdf_document <- pdf_text(name_of_input_PDF_file)
    # Convert to tibble so that tidyverse can be used
    pdf_document_tibble <- tibble(text = pdf_document)
    rm(pdf_document)
    # Each row is now a page of the PDF
    # Adding a column of the row numbers allows you to keep track of the page numbers
    pdf_document_tibble$pageNumbers <- 1:nrow(pdf_document_tibble)
    # Separate each line (of each page) into own row
    pdf_document_tibble <-
      separate_rows(pdf_document_tibble, text, sep = "\\n")

    # Identify page headers and footers and remove them
    pdf_document_tibble <- pdf_document_tibble %>%
      group_by(pageNumbers) %>%
      mutate(lineNumber = 1:n()) %>% # This gives you a line numbering for each page
      mutate(lastLine = n()) %>% # This tells you the number of the last line in each page
      ungroup()

    ## Identify front matter and remove it
    # Primarily identify the start of talking based on the first occurence of 'Mr SPEAKER'. 
    # It seems pretty common, but there are some misses (e.g. 1991-01-22). 
    # Use various backups
    pdf_document_tibble <- pdf_document_tibble %>%
      mutate(
        firstSpeakerRow = str_detect(text, "SPEAKER"),
        firstPresidentRow = str_detect(text, "PRESIDENT"),
        firstJointHouseRow = str_detect(text, "JOINT HOUSE"),
        firstTookTheChairRow = str_detect(text, "took the chair"),
        firstTheChairAtRow = str_detect(text, "the chair at")
      )
    pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == FALSE] <- NA
    pdf_document_tibble$firstPresidentRow[pdf_document_tibble$firstPresidentRow == FALSE] <- NA
    pdf_document_tibble$firstJointHouseRow[pdf_document_tibble$firstJointHouseRow == FALSE] <- NA
    pdf_document_tibble$firstTookTheChairRow[pdf_document_tibble$firstTookTheChairRow == FALSE] <- NA
    pdf_document_tibble$firstTheChairAtRow[pdf_document_tibble$firstTheChairAtRow == FALSE] <- NA

    # Get the row and corresponding page and then filter to only pages from that page
    row_of_first_SPEAKER <-
      pdf_document_tibble$firstSpeakerRow[pdf_document_tibble$firstSpeakerRow == TRUE] %>% which() %>% first()
    row_of_first_PRESIDENT <-
      pdf_document_tibble$firstPresidentRow[pdf_document_tibble$firstPresidentRow == TRUE] %>% which() %>% first()
    row_of_first_JOINTHOUSE <-
      pdf_document_tibble$firstJointHouseRow[pdf_document_tibble$firstJointHouseRow == TRUE] %>% which() %>% first()
    row_of_first_TookTheChair <-
      pdf_document_tibble$firstTookTheChairRow[pdf_document_tibble$firstTookTheChairRow == TRUE] %>% which() %>% first()
    row_of_first_TheChairAt <-
      pdf_document_tibble$firstTheChairAtRow[pdf_document_tibble$firstTheChairAtRow == TRUE] %>% which() %>% first()

    first_page_of_interest_SPEAKER <-
      pdf_document_tibble[row_of_first_SPEAKER, "pageNumbers"] %>% as.integer()
    first_page_of_interest_PRESIDENT <-
      pdf_document_tibble[row_of_first_PRESIDENT, "pageNumbers"] %>% as.integer()
    first_page_of_interest_JOINTHOUSE <-
      pdf_document_tibble[row_of_first_JOINTHOUSE, "pageNumbers"] %>% as.integer()
    first_page_of_interest_TookTheChair <-
      pdf_document_tibble[row_of_first_TookTheChair, "pageNumbers"] %>% as.integer()
    first_page_of_interest_TheChairAt <-
      pdf_document_tibble[row_of_first_TheChairAt, "pageNumbers"] %>% as.integer()

    first_page_of_interest_JOINTHOUSE <-
      (first_page_of_interest_JOINTHOUSE + 1)  %>% as.integer()

    filter_from_here <-
      case_when(
        !is.na(first_page_of_interest_TookTheChair) ~ first_page_of_interest_TookTheChair,
        !is.na(first_page_of_interest_TheChairAt) ~ first_page_of_interest_TheChairAt,
        !is.na(first_page_of_interest_SPEAKER) ~ first_page_of_interest_SPEAKER,
        !is.na(first_page_of_interest_PRESIDENT) ~ first_page_of_interest_PRESIDENT,
        TRUE ~ first_page_of_interest_JOINTHOUSE
      )

    pdf_document_tibble <- pdf_document_tibble %>%
      filter(pageNumbers >= filter_from_here) %>%
      select(-firstSpeakerRow,
             -firstPresidentRow,
             -firstJointHouseRow,
             -firstTookTheChairRow,
             -firstTheChairAtRow)

    # Save file
    write_csv(pdf_document_tibble, name_of_output_csv_file)
    # Helpful to know where you're up to
    print(paste0("Done with ", name_of_output_csv_file, " at ", Sys.time()))
  }

#### Walk through the lists and parse the PDFs ####
# Avoid errors
safely_get_text_from_PDFs <- safely(get_text_from_PDFs)

tic("Furrr walk2 stringr")
future_walk2(file_names,
             save_names,
             ~ safely_get_text_from_PDFs(.x, .y),
             .progress = TRUE)
toc()

@@

## Stopwords over time {#stopwordsgraph}
Insert the graph of stop words over time.

@@

# Topic modelling example and details {#LDAexample}

## Overview and example
As applied to Hansard, LDA considers each statement to be a result of a process where a politician first chooses the topics they want to speak about. After choosing the topics, the politician then chooses appropriate words to use for each of those topics. Statistically, LDA considers each document as having been generated by some probability distribution over topics. Similarly, each topic is considered a probability distribution over terms. To choose the terms used in each document, terms are picked from each topic in the appropriate proportion.

As an example, Figures \@ref(fig:topicsoverdocuments) and \@ref(fig:topicsoverterms) illustrate a smaller application with five topics, two documents, and ten terms. In this case, the first document may be comprised mostly of the first few topics; the other document may be mostly about the final few topics (Figure \@ref(fig:topicsoverdocuments)).

@@

## Document generation process

Gibbs sampling or the variational expectation-maximization algorithm can be used to approximate the posterior. A summary of these approaches is provided next.

@@

The choice of the number of topics, *k*, drives the results and must be specified *a priori*. If there is a strong reason for a particular number, then this can be used. Otherwise, one way to choose an appropriate number is to use cross validation. More detail on this process is provided in the next section.
